%!TEX TS-program = xelatex
\documentclass[]{zimine-cv}

\begin{document}

\header{Roman}{Zimine}

\pagecolor{bgbase1}

% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    \href{mailto:roman@zimine.ca}{roman@zimine.ca}
    437-580-4860
  \section{programming}
    C++, C, Go,
    Java, JavaScript,
    Python
  \section{technologies}
    Docker, Ember.js, PostgreSQL, Redis, Unreal Engine
\end{aside}

\section{interests}

algorithms, artificial intelligence, distributed systems, game development,\\
machine learning, systems programming


\section{experience}

\begin{entrylist}
  \entry
    {05/14-03/16}
    {Game Developer, Radiant Entertainment Inc.}
    {Los Altos, CA}
    {\begin{itemize}
      \item As the third engineer on the \hlref{http://www.pcgamer.com/rising-thunder-a-pc-only-fighting-game-from-experts-in-the-genre/}{Rising Thunder} team, took the game from prototype to an active alpha with millions of played matches.
      \item Led the integration of GGPO with Unreal Engine to create the best online experience in any fighting game to date.
      \item Integrated fixed-point math into Unreal Engine, and wrote a determenistic, fixed-point collision system.
      \item Worked with a designer to create the in-game UI (Ember.js).
      \item Made significant contributions to the server code (Go, C++) to improve matchmaking and stability.
    \end{itemize}}
  \entry
    {05/13-05/14}
    {Member of Technical Staff, VMware Inc.}
    {Palo Alto, CA}
    {\begin{itemize}
      \item Optimized and stabilized VMware Inventory Service for the vSphere 2015 release.
      \item Implemented internal query interface for vCenter.
      \item Reduced Inventory Service IO by 75\%, total vCenter Server IO by 35\%.
    \end{itemize}}
  \entry
    {05/12–08/12}
    {Engineering Intern, VMware Inc.}
    {Palo Alto, CA}
    {\begin{itemize}
      \item Ported the back-end database of VMware Inventory Service from xDB to MongoDB.
    \end{itemize}}
  \entry
    {05/11–08/11}
    {Engineering Intern, Google Inc.}
    {Mountain View, CA}
    {\begin{itemize}
      \item Designed and implemented code samples and documentation for the ST Coprocessor, an internal tool augmenting Megastore.
    \end{itemize}}
  \entry
    {05/10–08/10}
    {Engineering Intern, VMware Inc.}
    {Palo Alto, CA}
    {\begin{itemize}
      \item Designed and implemented code samples for the vSphere Web Services SDK.
    \end{itemize}}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2008-2013}
    {Honours BCS, University of Waterloo}
    {Waterloo, ON}
    {\begin{itemize}
       \item Computer Science Major, Classical Studies and Philosophy Minors
       \item 88\% GPA
    \end{itemize}}
\end{entrylist}

\section{projects}

\begin{itemize}[noitemsep]
  \item Implemented a small RPC library in C++.
  \item Added virtual memory and system calls to OS161.
  \item Participated in the 2012 Global Game Jam, developing a game in C++.
  \item Made a tetris clone with one-piece AI in C++.
  \item Implemented a small compiler in C.
\end{itemize}

\end{document}
